---
title: "Social Network Position and Strain Network Position"
author: "Francesco Beghini"
date: "2024-1-31"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```


```{r, echo=FALSE}
centrality_sim_df_covars_all <- readRDS('centrality_sim_df_covars_all.RDS')
sub_covar_centrality <- readRDS('sub_covar_centrality.RDS')
```

## Simple model
### Average strain-sharing rate to the rest of the villages, betweeness centrality
```{r}
lm.1 <- lmerTest::lmer(strain_sim_all ~ between_c_all + age_at_survey + household_wealth_index_w3 +
                         gender + DNA_conc + BMI + sampling_date + shipment_batch + Plate + WIKI + Reads + (1 | village) + (1|building_id),
             data = centrality_sim_df_covars_all)
summary(lm.1)
```

\newpage

### Average strain-sharing rate to the rest of the village, eigenvector centrality
```{r}
lm.1 <- lmerTest::lmer(strain_sim_all ~ eigen_c_all + age_at_survey +household_wealth_index_w3 +
                         gender+ DNA_conc + BMI + sampling_date + shipment_batch + Plate + WIKI + Reads +(1|village) + (1|building_id),
             data = centrality_sim_df_covars_all)
summary(lm.1)
```
\newpage
### Average strain-sharing rate to the rest of the village, degree
```{r}
lm.1 <- lmerTest::lmer(strain_sim_all ~ degree_c_all + age_at_survey +household_wealth_index_w3 +
                         gender+ DNA_conc + BMI + sampling_date + shipment_batch + Plate + WIKI + Reads + (1|village) + (1|building_id),
             data = centrality_sim_df_covars_all)
summary(lm.1)
```
\newpage

### First degree connections, clustering coefficient
```{r}
lm.1 <- lmerTest::lmer(sim_deg_one ~ cluster_coef_all + age_at_survey +household_wealth_index_w3 +
                         gender +  DNA_conc + BMI + sampling_date + shipment_batch + Plate + WIKI + Reads +(1|village_name) + (1|building_id),
             data = centrality_sim_df_covars_all)
summary(lm.1)
```
\newpage
### First degree connections, eigenvector centrality
```{r}
lm.1 <- lmerTest::lmer(sim_deg_one ~ eigen_c_all + age_at_survey +household_wealth_index_w3 +
                         gender+ DNA_conc + BMI + sampling_date + shipment_batch + Plate + WIKI + Reads +(1|village) + (1|building_id),
             data = centrality_sim_df_covars_all)
summary(lm.1)
```
\newpage
### First degree connections, betweeness centrality
```{r}
lm.1 <- lmerTest::lmer(sim_deg_one ~ between_c_all + age_at_survey +household_wealth_index_w3 +
                         gender+  DNA_conc + BMI + sampling_date + shipment_batch + Plate + WIKI + Reads +(1|village) + (1|building_id),
             data = centrality_sim_df_covars_all)
summary(lm.1)
```
\newpage
### First degree connections, degree
```{r}
lm.1 <- lmerTest::lmer(sim_deg_one ~ degree_c_all + age_at_survey +household_wealth_index_w3 +
                         gender+  DNA_conc + BMI + l0400 + mb_m0300 + sampling_date + shipment_batch + Plate + WIKI + Reads +(1|village) + (1|building_id),
             data = centrality_sim_df_covars_all)
summary(lm.1)
```
\newpage
## Separate covariates

## Average strain-sharing rate to the rest of the villages, betweeness centrality, use separate covariates
```{r}
lm.1 <- lmerTest::lmer(strain_sim_all ~ between_c_all + age_at_survey +household_wealth_index_w3 +DDS +med_painkillers +med_antibiotics+ med_antidiarrheal+ med_antiparasite+ med_vitamins+ med_zinc+ med_antifungal+ med_antihypertensives+ med_antidiabetics+ med_antiacids+ med_laxatives+ l0400+ mb_m0300 +
                         gender + DNA_conc + BMI + sampling_date + shipment_batch + Plate + WIKI + Reads +(1|village) + (1|building_id),
             data = centrality_sim_df_covars_all)
summary(lm.1)
```
\newpage
## Average strain-sharing rate to the rest of the village, eigenvector centrality, use separate covariates
```{r}
lm.1 <- lmerTest::lmer(strain_sim_all ~ eigen_c_all + age_at_survey +household_wealth_index_w3 +DDS +med_painkillers +med_antibiotics+ med_antidiarrheal+ med_antiparasite+ med_vitamins+ med_zinc+ med_antifungal+ med_antihypertensives+ med_antidiabetics+ med_antiacids+ med_laxatives+ l0400+ mb_m0300 +
                         gender+ DNA_conc + BMI + sampling_date + shipment_batch + Plate + WIKI + Reads +(1|village) + (1|building_id),
             data = centrality_sim_df_covars_all)
summary(lm.1)
```
\newpage
## Average strain-sharing rate to the rest of the village, degree, use separate covariates
```{r}
lm.1 <- lmerTest::lmer(strain_sim_all ~ degree_c_all + age_at_survey +household_wealth_index_w3 +DDS +med_painkillers +med_antibiotics+ med_antidiarrheal+ med_antiparasite+ med_vitamins+ med_zinc+ med_antifungal+ med_antihypertensives+ med_antidiabetics+ med_antiacids+ med_laxatives+ l0400+ mb_m0300 +
                         gender+ DNA_conc + BMI + sampling_date + shipment_batch + Plate + WIKI + Reads + (1|village) + (1|building_id),
             data = centrality_sim_df_covars_all)
summary(lm.1)
```
\newpage

## First degree connections, clustering coefficient, use separate covariates
```{r}
lm.1 <- lmerTest::lmer(sim_deg_one ~ cluster_coef_all + age_at_survey +household_wealth_index_w3 +DDS +med_painkillers +med_antibiotics+ med_antidiarrheal+ med_antiparasite+ med_vitamins+ med_zinc+ med_antifungal+ med_antihypertensives+ med_antidiabetics+ med_antiacids+ med_laxatives+ l0400+ mb_m0300 +
                         gender +  DNA_conc + BMI + sampling_date + shipment_batch + Plate + WIKI + Reads +(1|village_name) + (1|building_id),
             data = centrality_sim_df_covars_all)
summary(lm.1)
```
\newpage
## First degree connections, eigenvector centrality, use separate covariates
```{r}
lm.1 <- lmerTest::lmer(sim_deg_one ~ eigen_c_all + age_at_survey +household_wealth_index_w3 +DDS +med_painkillers +med_antibiotics+ med_antidiarrheal+ med_antiparasite+ med_vitamins+ med_zinc+ med_antifungal+ med_antihypertensives+ med_antidiabetics+ med_antiacids+ med_laxatives+ l0400+ mb_m0300 +
                         gender+ DNA_conc + BMI + sampling_date + shipment_batch + Plate + WIKI + Reads +(1|village) + (1|building_id),
             data = centrality_sim_df_covars_all)
summary(lm.1)
```
\newpage
## First degree connections, betweeness centrality, use separate covariates
```{r}
lm.1 <- lmerTest::lmer(sim_deg_one ~ between_c_all + age_at_survey +household_wealth_index_w3 +DDS +med_painkillers +med_antibiotics+ med_antidiarrheal+ med_antiparasite+ med_vitamins+ med_zinc+ med_antifungal+ med_antihypertensives+ med_antidiabetics+ med_antiacids+ med_laxatives+ l0400+ mb_m0300 +
                         gender+  DNA_conc + BMI + sampling_date + shipment_batch + Plate + WIKI + Reads +(1|village) + (1|building_id),
             data = centrality_sim_df_covars_all)
summary(lm.1)
```
\newpage
## First degree connections, degree, use separate covariates
```{r}
lm.1 <- lmerTest::lmer(sim_deg_one ~ degree_c_all + age_at_survey +household_wealth_index_w3 +DDS +med_painkillers +med_antibiotics+ med_antidiarrheal+ med_antiparasite+ med_vitamins+ med_zinc+ med_antifungal+ med_antihypertensives+ med_antidiabetics+ med_antiacids+ med_laxatives+ l0400+ mb_m0300 +
                         gender+  DNA_conc + BMI + l0400 + mb_m0300 + sampling_date + shipment_batch + Plate + WIKI + Reads +(1|village) + (1|building_id),
             data = centrality_sim_df_covars_all)
summary(lm.1)
```
\newpage

## Mahalanobis
## Average strain-sharing rate to the rest of the villages, betweeness centrality, use Mahalanobis distance
```{r}
lm.1 <- lmerTest::lmer(strain_sim_all ~ between_c_all + maha_social + DNA_conc + sampling_date + shipment_batch + Plate + WIKI + Reads +(1|village) + (1|building_id),
             data = dplyr::bind_cols(centrality_sim_df_covars_all, maha_social = mahalanobis(sub_covar_centrality, FALSE, var(sub_covar_centrality, na.rm=TRUE)))
)
summary(lm.1)
```
\newpage
## Average strain-sharing rate to the rest of the village, eigenvector centrality, use Mahalanobis distance
```{r}
lm.1 <- lmerTest::lmer(strain_sim_all ~ eigen_c_all + maha_social + DNA_conc + sampling_date + shipment_batch + Plate + WIKI + Reads +(1|village) + (1|building_id),
             data = dplyr::bind_cols(centrality_sim_df_covars_all, maha_social = mahalanobis(sub_covar_centrality, FALSE, var(sub_covar_centrality, na.rm=TRUE)))
)
summary(lm.1)
```
\newpage
## Average strain-sharing rate to the rest of the village, degree, use Mahalanobis distance
```{r}
lm.1 <- lmerTest::lmer(strain_sim_all ~ degree_c_all + maha_social + DNA_conc + sampling_date + shipment_batch + Plate + WIKI + Reads + (1|village) + (1|building_id),
             data = dplyr::bind_cols(centrality_sim_df_covars_all, maha_social = mahalanobis(sub_covar_centrality, FALSE, var(sub_covar_centrality, na.rm=TRUE)))
)
summary(lm.1)
```
\newpage

## First degree connections, clustering coefficient, use Mahalanobis distance
```{r}
lm.1 <- lmerTest::lmer(sim_deg_one ~ cluster_coef_all + maha_social + DNA_conc + sampling_date + shipment_batch + Plate + WIKI + Reads +(1|village_name) + (1|building_id),
             data = dplyr::bind_cols(centrality_sim_df_covars_all, maha_social = mahalanobis(sub_covar_centrality, FALSE, var(sub_covar_centrality, na.rm=TRUE)))
)
summary(lm.1)
```
\newpage
## First degree connections, eigenvector centrality, use Mahalanobis distance
```{r}
lm.1 <- lmerTest::lmer(sim_deg_one ~ eigen_c_all + maha_social + DNA_conc + sampling_date + shipment_batch + Plate + WIKI + Reads +(1|village) + (1|building_id),
             data = dplyr::bind_cols(centrality_sim_df_covars_all, maha_social = mahalanobis(sub_covar_centrality, FALSE, var(sub_covar_centrality, na.rm=TRUE)))
)
summary(lm.1)
```
\newpage
## First degree connections, betweeness centrality, use Mahalanobis distance
```{r}
lm.1 <- lmerTest::lmer(sim_deg_one ~ between_c_all + maha_social + DNA_conc  + sampling_date + shipment_batch + Plate + WIKI + Reads +(1|village) + (1|building_id),
             data = dplyr::bind_cols(centrality_sim_df_covars_all, maha_social = mahalanobis(sub_covar_centrality, FALSE, var(sub_covar_centrality, na.rm=TRUE)))
)
summary(lm.1)
```
\newpage
## First degree connections, degree, use Mahalanobis distance
```{r}
lm.1 <- lmerTest::lmer(sim_deg_one ~ degree_c_all + maha_social + DNA_conc + sampling_date + shipment_batch + Plate + WIKI + Reads +(1|village) + (1|building_id),
             data = dplyr::bind_cols(centrality_sim_df_covars_all, maha_social = mahalanobis(sub_covar_centrality, FALSE, var(sub_covar_centrality, na.rm=TRUE)))
             )

summary(lm.1)
```
