---
title: "Clustering"
author: "Jackson Pullman"
date: "2022-12-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Clustering
library(ggplotify)
#Imports Rand Index
library(mclust)
#citation("mclust")
#Get observed metric

set.seed(1)
#Louvain clustering does not work with NA edge weights, set to zero
E(strain_rate_vil_graph_1)$weight[is.na(E(strain_rate_vil_graph_1)$weight)] <- 0
E(strain_rate_vil_graph_2)$weight[is.na(E(strain_rate_vil_graph_2)$weight)] <- 0
E(strain_rate_vil_graph_3)$weight[is.na(E(strain_rate_vil_graph_3)$weight)] <- 0
E(strain_rate_vil_graph_4)$weight[is.na(E(strain_rate_vil_graph_4)$weight)] <- 0
E(strain_rate_vil_graph_5)$weight[is.na(E(strain_rate_vil_graph_5)$weight)] <- 0
E(strain_rate_vil_graph_6)$weight[is.na(E(strain_rate_vil_graph_6)$weight)] <- 0
E(strain_rate_vil_graph_7)$weight[is.na(E(strain_rate_vil_graph_7)$weight)] <- 0
E(strain_rate_vil_graph_8)$weight[is.na(E(strain_rate_vil_graph_8)$weight)] <- 0
E(strain_rate_vil_graph_9)$weight[is.na(E(strain_rate_vil_graph_9)$weight)] <- 0
E(strain_rate_vil_graph_10)$weight[is.na(E(strain_rate_vil_graph_10)$weight)] <- 0
E(strain_rate_vil_graph_11)$weight[is.na(E(strain_rate_vil_graph_11)$weight)] <- 0
E(strain_rate_vil_graph_12)$weight[is.na(E(strain_rate_vil_graph_12)$weight)] <- 0
E(strain_rate_vil_graph_13)$weight[is.na(E(strain_rate_vil_graph_13)$weight)] <- 0
E(strain_rate_vil_graph_14)$weight[is.na(E(strain_rate_vil_graph_14)$weight)] <- 0
E(strain_rate_vil_graph_15)$weight[is.na(E(strain_rate_vil_graph_15)$weight)] <- 0
E(strain_rate_vil_graph_16)$weight[is.na(E(strain_rate_vil_graph_16)$weight)] <- 0
E(strain_rate_vil_graph_17)$weight[is.na(E(strain_rate_vil_graph_17)$weight)] <- 0
E(strain_rate_vil_graph_18)$weight[is.na(E(strain_rate_vil_graph_18)$weight)] <- 0

for(i in 1:length(village_names)){
  assign(paste0("strain_rate_vil_graph_scram_", i), get(paste0("strain_rate_vil_graph_", i)))
}


strain_rate_cluster_1 <- cluster_louvain(strain_rate_vil_graph_1, weights = E(strain_rate_vil_graph_1)$weight)
strain_rate_cluster_2 <- cluster_louvain(strain_rate_vil_graph_2, weights = E(strain_rate_vil_graph_2)$weight)
strain_rate_cluster_3 <- cluster_louvain(strain_rate_vil_graph_3, weights = E(strain_rate_vil_graph_3)$weight)
strain_rate_cluster_4 <- cluster_louvain(strain_rate_vil_graph_4, weights = E(strain_rate_vil_graph_4)$weight)
strain_rate_cluster_5 <- cluster_louvain(strain_rate_vil_graph_5, weights = E(strain_rate_vil_graph_5)$weight)
strain_rate_cluster_6 <- cluster_louvain(strain_rate_vil_graph_6, weights = E(strain_rate_vil_graph_6)$weight)
strain_rate_cluster_7 <- cluster_louvain(strain_rate_vil_graph_7, weights = E(strain_rate_vil_graph_7)$weight)
strain_rate_cluster_8 <- cluster_louvain(strain_rate_vil_graph_8, weights = E(strain_rate_vil_graph_8)$weight)
strain_rate_cluster_9 <- cluster_louvain(strain_rate_vil_graph_9, weights = E(strain_rate_vil_graph_9)$weight)
strain_rate_cluster_10 <- cluster_louvain(strain_rate_vil_graph_10, weights = E(strain_rate_vil_graph_10)$weight)
strain_rate_cluster_11 <- cluster_louvain(strain_rate_vil_graph_11, weights = E(strain_rate_vil_graph_11)$weight)
strain_rate_cluster_12 <- cluster_louvain(strain_rate_vil_graph_12, weights = E(strain_rate_vil_graph_12)$weight)
strain_rate_cluster_13 <- cluster_louvain(strain_rate_vil_graph_13, weights = E(strain_rate_vil_graph_13)$weight)
strain_rate_cluster_14 <- cluster_louvain(strain_rate_vil_graph_14, weights = E(strain_rate_vil_graph_14)$weight)
strain_rate_cluster_15 <- cluster_louvain(strain_rate_vil_graph_15, weights = E(strain_rate_vil_graph_15)$weight)
strain_rate_cluster_16 <- cluster_louvain(strain_rate_vil_graph_16, weights = E(strain_rate_vil_graph_16)$weight)
strain_rate_cluster_17 <- cluster_louvain(strain_rate_vil_graph_17, weights = E(strain_rate_vil_graph_17)$weight)
strain_rate_cluster_18 <- cluster_louvain(strain_rate_vil_graph_18, weights = E(strain_rate_vil_graph_18)$weight)

#Get microbiome clustering for each village based on count of shared strains

set.seed(1)
#Get social network clustering for each village
sn_cluster_1 <- cluster_louvain(sn_vil_graph_1)
sn_cluster_2 <- cluster_louvain(sn_vil_graph_2)
sn_cluster_3 <- cluster_louvain(sn_vil_graph_3)
sn_cluster_4 <- cluster_louvain(sn_vil_graph_4)
sn_cluster_5 <- cluster_louvain(sn_vil_graph_5)
sn_cluster_6 <- cluster_louvain(sn_vil_graph_6)
sn_cluster_7 <- cluster_louvain(sn_vil_graph_7)
sn_cluster_8 <- cluster_louvain(sn_vil_graph_8)
sn_cluster_9 <- cluster_louvain(sn_vil_graph_9)
sn_cluster_10 <- cluster_louvain(sn_vil_graph_10)
sn_cluster_11 <- cluster_louvain(sn_vil_graph_11)
sn_cluster_12 <- cluster_louvain(sn_vil_graph_12)
sn_cluster_13 <- cluster_louvain(sn_vil_graph_13)
sn_cluster_14 <- cluster_louvain(sn_vil_graph_14)
sn_cluster_15 <- cluster_louvain(sn_vil_graph_15)
sn_cluster_16 <- cluster_louvain(sn_vil_graph_16)
sn_cluster_17 <- cluster_louvain(sn_vil_graph_17)
sn_cluster_18 <- cluster_louvain(sn_vil_graph_18)


#Order names for both clusters
mbiome_member_1 <- membership(strain_rate_cluster_1)[match(names(membership(sn_cluster_1)),
                                                           names(membership(strain_rate_cluster_1)))]
mbiome_member_2 <- membership(strain_rate_cluster_2)[match(names(membership(sn_cluster_2)),
                                                           names(membership(strain_rate_cluster_2)))]
mbiome_member_3 <- membership(strain_rate_cluster_3)[match(names(membership(sn_cluster_3)),
                                                           names(membership(strain_rate_cluster_3)))]
mbiome_member_4 <- membership(strain_rate_cluster_4)[match(names(membership(sn_cluster_4)),
                                                           names(membership(strain_rate_cluster_4)))]
mbiome_member_5 <- membership(strain_rate_cluster_5)[match(names(membership(sn_cluster_5)),
                                                           names(membership(strain_rate_cluster_5)))]
mbiome_member_6 <- membership(strain_rate_cluster_6)[match(names(membership(sn_cluster_6)),
                                                           names(membership(strain_rate_cluster_6)))]
mbiome_member_7 <- membership(strain_rate_cluster_7)[match(names(membership(sn_cluster_7)),
                                                           names(membership(strain_rate_cluster_7)))]
mbiome_member_8 <- membership(strain_rate_cluster_8)[match(names(membership(sn_cluster_8)),
                                                           names(membership(strain_rate_cluster_8)))]
mbiome_member_9 <- membership(strain_rate_cluster_9)[match(names(membership(sn_cluster_9)),
                                                           names(membership(strain_rate_cluster_9)))]
mbiome_member_10 <- membership(strain_rate_cluster_10)[match(names(membership(sn_cluster_10)),
                                                           names(membership(strain_rate_cluster_10)))]
mbiome_member_11 <- membership(strain_rate_cluster_11)[match(names(membership(sn_cluster_11)),
                                                           names(membership(strain_rate_cluster_11)))]
mbiome_member_12 <- membership(strain_rate_cluster_12)[match(names(membership(sn_cluster_12)),
                                                           names(membership(strain_rate_cluster_12)))]
mbiome_member_13 <- membership(strain_rate_cluster_13)[match(names(membership(sn_cluster_13)),
                                                           names(membership(strain_rate_cluster_13)))]
mbiome_member_14 <- membership(strain_rate_cluster_14)[match(names(membership(sn_cluster_14)),
                                                           names(membership(strain_rate_cluster_14)))]
mbiome_member_15 <- membership(strain_rate_cluster_15)[match(names(membership(sn_cluster_15)),
                                                           names(membership(strain_rate_cluster_15)))]
mbiome_member_16 <- membership(strain_rate_cluster_16)[match(names(membership(sn_cluster_16)),
                                                           names(membership(strain_rate_cluster_16)))]
mbiome_member_17 <- membership(strain_rate_cluster_17)[match(names(membership(sn_cluster_17)),
                                                           names(membership(strain_rate_cluster_17)))]
mbiome_member_18 <- membership(strain_rate_cluster_18)[match(names(membership(sn_cluster_18)),
                                                           names(membership(strain_rate_cluster_18)))]


#adjust village cluster numbers so the are different across villages
mbiome_member_1 <- mbiome_member_1 + 100
mbiome_member_2 <- mbiome_member_2 + 200
mbiome_member_3 <- mbiome_member_3 + 300
mbiome_member_4 <- mbiome_member_4 + 400
mbiome_member_5 <- mbiome_member_5 + 500
mbiome_member_6 <- mbiome_member_6 + 600
mbiome_member_7 <- mbiome_member_7 + 700
mbiome_member_8 <- mbiome_member_8 + 800
mbiome_member_9 <- mbiome_member_9 + 900
mbiome_member_10 <- mbiome_member_10 + 1000
mbiome_member_11 <- mbiome_member_11 + 1100
mbiome_member_12 <- mbiome_member_12 + 1200
mbiome_member_13 <- mbiome_member_13 + 1300
mbiome_member_14 <- mbiome_member_14 + 1400
mbiome_member_15 <- mbiome_member_15 + 1500
mbiome_member_16 <- mbiome_member_16 + 1600
mbiome_member_17 <- mbiome_member_17 + 1700
mbiome_member_18 <- mbiome_member_18 + 1800


#Create social network membership vectors, shifted by village
sn_member_1 <- membership(sn_cluster_1) + 100
sn_member_2 <- membership(sn_cluster_2) + 200
sn_member_3 <- membership(sn_cluster_3) + 300
sn_member_4 <- membership(sn_cluster_4) + 400
sn_member_5 <- membership(sn_cluster_5) + 500
sn_member_6 <- membership(sn_cluster_6) + 600
sn_member_7 <- membership(sn_cluster_7) + 700
sn_member_8 <- membership(sn_cluster_8) + 800
sn_member_9 <- membership(sn_cluster_9) + 900
sn_member_10 <- membership(sn_cluster_10) + 1000
sn_member_11 <- membership(sn_cluster_11) + 1100
sn_member_12 <- membership(sn_cluster_12) + 1200
sn_member_13 <- membership(sn_cluster_13) + 1300
sn_member_14 <- membership(sn_cluster_14) + 1400
sn_member_15 <- membership(sn_cluster_15) + 1500
sn_member_16 <- membership(sn_cluster_16) + 1600
sn_member_17 <- membership(sn_cluster_17) + 1700
sn_member_18 <- membership(sn_cluster_18) + 1800


#Get rand index across all villages
all_mbiome_membership <-c(mbiome_member_1,
                          mbiome_member_2,
                          mbiome_member_3,
                          mbiome_member_4,
                          mbiome_member_5,
                          mbiome_member_6,
                          mbiome_member_7,
                          mbiome_member_8,
                          mbiome_member_9,
                          mbiome_member_10,
                          mbiome_member_11,
                          mbiome_member_12,
                          mbiome_member_13,
                          mbiome_member_14,
                          mbiome_member_15,
                          mbiome_member_16,
                          mbiome_member_17,
                          mbiome_member_18)

all_sn_membership <- c(sn_member_1,
                       sn_member_2,
                       sn_member_3,
                       sn_member_4,
                       sn_member_5,
                       sn_member_6,
                       sn_member_7,
                       sn_member_8,
                       sn_member_9,
                       sn_member_10,
                       sn_member_11,
                       sn_member_12,
                       sn_member_13,
                       sn_member_14,
                       sn_member_15,
                       sn_member_16,
                       sn_member_17,
                       sn_member_18)
```

#Get Statistics on clustering
```{r}
all_sn_membership_df <- data.frame(name = names(all_sn_membership),
                                   cluster = unname(all_sn_membership))

all_mbiome_membership_df <- data.frame(name = names(all_mbiome_membership),
                                   cluster = unname(all_mbiome_membership))
```

#Average number of people in social network clusters
```{r}
all_sn_membership_df %>%
  group_by(cluster) %>%
  summarize(n = n()) %>%
  summarise(mean(n), median(n), sd(n))
```

#Average number of people in strain-sharing network clusters
```{r}
all_mbiome_membership_df %>%
  group_by(cluster) %>%
  summarize(n = n()) %>%
  summarise(mean(n), median(n), sd(n))
```

```{r}
all_mbiome_membership_df %>%
  group_by(cluster) %>%
  summarize(n = n()) %>%
  arrange(n)
```

#Average strain-sharing rate within cluster
```{r}
uniq_clusters <- unique(all_mbiome_membership_df$cluster)
cluster_sharing_all <- c()
for(i in 1:length(uniq_clusters)){
  cluster_names <- all_mbiome_membership_df %>% filter(cluster == uniq_clusters[i]) %>% pull(name)
  cluster_sharing <- strain_rate[rownames(strain_rate) %in% cluster_names,
                                 colnames(strain_rate) %in% cluster_names]
  cluster_sharing[lower.tri(cluster_sharing, diag = TRUE)] <- NA
  #cluster_sharing_all <- c(cluster_sharing_all,
   #                        na.omit(unlist(as.list(cluster_sharing))))
  cluster_sharing_all <- c(cluster_sharing_all,
                           mean(unlist(as.list(cluster_sharing)), na.rm = TRUE))
  
}
median(cluster_sharing_all, na.rm = TRUE)
```

#Average number of ties
```{r}
uniq_clusters <- unique(all_sn_membership_df$cluster)
cluster_ties_all <- c()

SN_Graph_all <- as_adjacency_matrix(simplify(graph_from_data_frame(SN, directed = FALSE)))

for(i in 1:length(uniq_clusters)){
  cluster_names <- all_sn_membership_df %>% filter(cluster == uniq_clusters[i]) %>% pull(name)
  cluster_count <- SN_Graph_all[rownames(SN_Graph_all) %in% cluster_names,
                                 colnames(SN_Graph_all) %in% cluster_names]
  cluster_count[lower.tri(cluster_count, diag = TRUE)] <- NA
  #cluster_sharing_all <- c(cluster_sharing_all,
   #                        na.omit(unlist(as.list(cluster_sharing))))
  cluster_ties_all <- c(cluster_ties_all,
                           sum(unlist(as.list(cluster_count)), na.rm = TRUE))
  
}
mean(cluster_ties_all)
```

```{r}
rand_stat_strain_rate <- mclust::adjustedRandIndex(all_mbiome_membership, all_sn_membership)

null_rands_strain_rate <- numeric(10000)

#Create null distribution metrics
cl <- parallel::makeCluster(10)
doParallel::registerDoParallel(cl)
foreach(i= c(1:10000), .combine=rbind, .packages = c('igraph') ) %dopar% {
  #Scramble microbiome
  strain_rate_vil_graph_scram_1 <- set.vertex.attribute(strain_rate_vil_graph_scram_1, "name",
                                                        value = sample(vertex_attr(strain_rate_vil_graph_scram_1, "name")))
  strain_rate_vil_graph_scram_2 <- set.vertex.attribute(strain_rate_vil_graph_scram_2, "name",
                                                        value = sample(vertex_attr(strain_rate_vil_graph_scram_2, "name")))
  strain_rate_vil_graph_scram_3 <- set.vertex.attribute(strain_rate_vil_graph_scram_3, "name",
                                                        value = sample(vertex_attr(strain_rate_vil_graph_scram_3, "name")))
  strain_rate_vil_graph_scram_4 <- set.vertex.attribute(strain_rate_vil_graph_scram_4, "name",
                                                        value = sample(vertex_attr(strain_rate_vil_graph_scram_4, "name")))
  strain_rate_vil_graph_scram_5 <- set.vertex.attribute(strain_rate_vil_graph_scram_5, "name",
                                                        value = sample(vertex_attr(strain_rate_vil_graph_scram_5, "name")))
  strain_rate_vil_graph_scram_6 <- set.vertex.attribute(strain_rate_vil_graph_scram_6, "name",
                                                        value = sample(vertex_attr(strain_rate_vil_graph_scram_6, "name")))
  strain_rate_vil_graph_scram_7 <- set.vertex.attribute(strain_rate_vil_graph_scram_7, "name",
                                                        value = sample(vertex_attr(strain_rate_vil_graph_scram_7, "name")))
  strain_rate_vil_graph_scram_8 <- set.vertex.attribute(strain_rate_vil_graph_scram_8, "name",
                                                        value = sample(vertex_attr(strain_rate_vil_graph_scram_8, "name")))
  strain_rate_vil_graph_scram_9 <- set.vertex.attribute(strain_rate_vil_graph_scram_9, "name",
                                                        value = sample(vertex_attr(strain_rate_vil_graph_scram_9, "name")))
  strain_rate_vil_graph_scram_10 <- set.vertex.attribute(strain_rate_vil_graph_scram_10, "name",
                                                        value = sample(vertex_attr(strain_rate_vil_graph_scram_10, "name")))
  strain_rate_vil_graph_scram_11 <- set.vertex.attribute(strain_rate_vil_graph_scram_11, "name",
                                                        value = sample(vertex_attr(strain_rate_vil_graph_scram_11, "name")))
  strain_rate_vil_graph_scram_12 <- set.vertex.attribute(strain_rate_vil_graph_scram_12, "name",
                                                        value = sample(vertex_attr(strain_rate_vil_graph_scram_12, "name")))
  strain_rate_vil_graph_scram_13 <- set.vertex.attribute(strain_rate_vil_graph_scram_13, "name",
                                                        value = sample(vertex_attr(strain_rate_vil_graph_scram_13, "name")))
  strain_rate_vil_graph_scram_14 <- set.vertex.attribute(strain_rate_vil_graph_scram_14, "name",
                                                        value = sample(vertex_attr(strain_rate_vil_graph_scram_14, "name")))
  strain_rate_vil_graph_scram_15 <- set.vertex.attribute(strain_rate_vil_graph_scram_15, "name",
                                                        value = sample(vertex_attr(strain_rate_vil_graph_scram_15, "name")))
  strain_rate_vil_graph_scram_16 <- set.vertex.attribute(strain_rate_vil_graph_scram_16, "name",
                                                        value = sample(vertex_attr(strain_rate_vil_graph_scram_16, "name")))
  strain_rate_vil_graph_scram_17 <- set.vertex.attribute(strain_rate_vil_graph_scram_17, "name",
                                                        value = sample(vertex_attr(strain_rate_vil_graph_scram_17, "name")))
  strain_rate_vil_graph_scram_18 <- set.vertex.attribute(strain_rate_vil_graph_scram_18, "name",
                                                        value = sample(vertex_attr(strain_rate_vil_graph_scram_18, "name")))
  
  #Get scrambled microbiome membership
  
  strain_rate_cluster_1_scram <- cluster_louvain(strain_rate_vil_graph_scram_1, weights = E(strain_rate_vil_graph_scram_1)$weight)
  strain_rate_cluster_2_scram <- cluster_louvain(strain_rate_vil_graph_scram_2, weights = E(strain_rate_vil_graph_scram_2)$weight)
  strain_rate_cluster_3_scram <- cluster_louvain(strain_rate_vil_graph_scram_3, weights = E(strain_rate_vil_graph_scram_3)$weight)
  strain_rate_cluster_4_scram <- cluster_louvain(strain_rate_vil_graph_scram_4, weights = E(strain_rate_vil_graph_scram_4)$weight)
  strain_rate_cluster_5_scram <- cluster_louvain(strain_rate_vil_graph_scram_5, weights = E(strain_rate_vil_graph_scram_5)$weight)
  strain_rate_cluster_6_scram <- cluster_louvain(strain_rate_vil_graph_scram_6, weights = E(strain_rate_vil_graph_scram_6)$weight)
  strain_rate_cluster_7_scram <- cluster_louvain(strain_rate_vil_graph_scram_7, weights = E(strain_rate_vil_graph_scram_7)$weight)
  strain_rate_cluster_8_scram <- cluster_louvain(strain_rate_vil_graph_scram_8, weights = E(strain_rate_vil_graph_scram_8)$weight)
  strain_rate_cluster_9_scram <- cluster_louvain(strain_rate_vil_graph_scram_9, weights = E(strain_rate_vil_graph_scram_9)$weight)
  strain_rate_cluster_10_scram <- cluster_louvain(strain_rate_vil_graph_scram_10, weights = E(strain_rate_vil_graph_scram_10)$weight)
  strain_rate_cluster_11_scram <- cluster_louvain(strain_rate_vil_graph_scram_11, weights = E(strain_rate_vil_graph_scram_11)$weight)
  strain_rate_cluster_12_scram <- cluster_louvain(strain_rate_vil_graph_scram_12, weights = E(strain_rate_vil_graph_scram_12)$weight)
  strain_rate_cluster_13_scram <- cluster_louvain(strain_rate_vil_graph_scram_13, weights = E(strain_rate_vil_graph_scram_13)$weight)
  strain_rate_cluster_14_scram <- cluster_louvain(strain_rate_vil_graph_scram_14, weights = E(strain_rate_vil_graph_scram_14)$weight)
  strain_rate_cluster_15_scram <- cluster_louvain(strain_rate_vil_graph_scram_15, weights = E(strain_rate_vil_graph_scram_15)$weight)
  strain_rate_cluster_16_scram <- cluster_louvain(strain_rate_vil_graph_scram_16, weights = E(strain_rate_vil_graph_scram_16)$weight)
  strain_rate_cluster_17_scram <- cluster_louvain(strain_rate_vil_graph_scram_17, weights = E(strain_rate_vil_graph_scram_17)$weight)
  strain_rate_cluster_18_scram <- cluster_louvain(strain_rate_vil_graph_scram_18, weights = E(strain_rate_vil_graph_scram_18)$weight)

  
  #Order scrambled microbiome membership and make separate by villages
  mbiome_member_1_scram <- membership(strain_rate_cluster_1_scram)[match(names(membership(sn_cluster_1)),
                                                             names(membership(strain_rate_cluster_1_scram)))] + 100
  mbiome_member_2_scram <- membership(strain_rate_cluster_2_scram)[match(names(membership(sn_cluster_2)),
                                                             names(membership(strain_rate_cluster_2_scram)))] + 200
  mbiome_member_3_scram <- membership(strain_rate_cluster_3_scram)[match(names(membership(sn_cluster_3)),
                                                             names(membership(strain_rate_cluster_3_scram)))] + 300
  mbiome_member_4_scram <- membership(strain_rate_cluster_4_scram)[match(names(membership(sn_cluster_4)),
                                                             names(membership(strain_rate_cluster_4_scram)))] + 400
  mbiome_member_5_scram <- membership(strain_rate_cluster_5_scram)[match(names(membership(sn_cluster_5)),
                                                             names(membership(strain_rate_cluster_5_scram)))] + 500
  mbiome_member_6_scram <- membership(strain_rate_cluster_6_scram)[match(names(membership(sn_cluster_6)),
                                                             names(membership(strain_rate_cluster_6_scram)))] + 600
  mbiome_member_7_scram <- membership(strain_rate_cluster_7_scram)[match(names(membership(sn_cluster_7)),
                                                             names(membership(strain_rate_cluster_7_scram)))] + 700
  mbiome_member_8_scram <- membership(strain_rate_cluster_8_scram)[match(names(membership(sn_cluster_8)),
                                                             names(membership(strain_rate_cluster_8_scram)))] + 800
  mbiome_member_9_scram <- membership(strain_rate_cluster_9_scram)[match(names(membership(sn_cluster_9)),
                                                             names(membership(strain_rate_cluster_9_scram)))] + 900
  mbiome_member_10_scram <- membership(strain_rate_cluster_10_scram)[match(names(membership(sn_cluster_10)),
                                                             names(membership(strain_rate_cluster_10_scram)))] + 1000
  mbiome_member_11_scram <- membership(strain_rate_cluster_11_scram)[match(names(membership(sn_cluster_11)),
                                                             names(membership(strain_rate_cluster_11_scram)))] + 1100
  mbiome_member_12_scram <- membership(strain_rate_cluster_12_scram)[match(names(membership(sn_cluster_12)),
                                                             names(membership(strain_rate_cluster_12_scram)))] + 1200
  mbiome_member_13_scram <- membership(strain_rate_cluster_13_scram)[match(names(membership(sn_cluster_13)),
                                                             names(membership(strain_rate_cluster_13_scram)))] + 1300
  mbiome_member_14_scram <- membership(strain_rate_cluster_14_scram)[match(names(membership(sn_cluster_14)),
                                                             names(membership(strain_rate_cluster_14_scram)))] + 1400
  mbiome_member_15_scram <- membership(strain_rate_cluster_15_scram)[match(names(membership(sn_cluster_15)),
                                                             names(membership(strain_rate_cluster_15_scram)))] + 1500
  mbiome_member_16_scram <- membership(strain_rate_cluster_16_scram)[match(names(membership(sn_cluster_16)),
                                                             names(membership(strain_rate_cluster_16_scram)))] + 1600
  mbiome_member_17_scram <- membership(strain_rate_cluster_17_scram)[match(names(membership(sn_cluster_17)),
                                                             names(membership(strain_rate_cluster_17_scram)))] + 1700
  mbiome_member_18_scram <- membership(strain_rate_cluster_18_scram)[match(names(membership(sn_cluster_18)),
                                                             names(membership(strain_rate_cluster_18_scram)))] + 1800
  
  #combine membership
  all_mbiome_membership_scram <-c(mbiome_member_1_scram,
                            mbiome_member_2_scram,
                            mbiome_member_3_scram,
                            mbiome_member_4_scram,
                            mbiome_member_5_scram,
                            mbiome_member_6_scram,
                            mbiome_member_7_scram,
                            mbiome_member_8_scram,
                            mbiome_member_9_scram,
                            mbiome_member_10_scram,
                            mbiome_member_11_scram,
                            mbiome_member_12_scram,
                            mbiome_member_13_scram,
                            mbiome_member_14_scram,
                            mbiome_member_15_scram,
                            mbiome_member_16_scram,
                            mbiome_member_17_scram,
                            mbiome_member_18_scram)

  #Get null statistic
  null_rands_strain_rate[i] <- mclust::adjustedRandIndex(all_mbiome_membership_scram, all_sn_membership)

    data.frame(rand_inds = c(mclust::adjustedRandIndex(mbiome_member_1_scram, sn_member_1),
                                              mclust::adjustedRandIndex(mbiome_member_2_scram, sn_member_2),
                                              mclust::adjustedRandIndex(mbiome_member_3_scram, sn_member_3),
                                              mclust::adjustedRandIndex(mbiome_member_4_scram, sn_member_4),
                                              mclust::adjustedRandIndex(mbiome_member_5_scram, sn_member_5),
                                              mclust::adjustedRandIndex(mbiome_member_6_scram, sn_member_6),
                                              mclust::adjustedRandIndex(mbiome_member_7_scram, sn_member_7),
                                              mclust::adjustedRandIndex(mbiome_member_8_scram, sn_member_8),
                                              mclust::adjustedRandIndex(mbiome_member_9_scram, sn_member_9),
                                              mclust::adjustedRandIndex(mbiome_member_10_scram, sn_member_10),
                                              mclust::adjustedRandIndex(mbiome_member_11_scram, sn_member_11),
                                              mclust::adjustedRandIndex(mbiome_member_12_scram, sn_member_12),
                                              mclust::adjustedRandIndex(mbiome_member_13_scram, sn_member_13),
                                              mclust::adjustedRandIndex(mbiome_member_14_scram, sn_member_14),
                                              mclust::adjustedRandIndex(mbiome_member_15_scram, sn_member_15),
                                              mclust::adjustedRandIndex(mbiome_member_16_scram, sn_member_16),
                                              mclust::adjustedRandIndex(mbiome_member_17_scram, sn_member_17),
                                              mclust::adjustedRandIndex(mbiome_member_18_scram, sn_member_18)),
                                vils = village_names)
} -> null_clusters
null_clusters$vils <- village_map$village_name_deid[match(null_clusters$vils, village_map$village_code)]

parallel::stopCluster(cl)
```


```{r}
village_names_temp <- village_names
observed <- data.frame(
  vils = village_map$village_name_deid[match(village_names_temp, village_map$village_code)],
  obs = c(
    mclust::adjustedRandIndex(mbiome_member_1, sn_member_1),
    mclust::adjustedRandIndex(mbiome_member_2, sn_member_2),
    mclust::adjustedRandIndex(mbiome_member_3, sn_member_3),
    mclust::adjustedRandIndex(mbiome_member_4, sn_member_4),
    mclust::adjustedRandIndex(mbiome_member_5, sn_member_5),
    mclust::adjustedRandIndex(mbiome_member_6, sn_member_6),
    mclust::adjustedRandIndex(mbiome_member_7, sn_member_7),
    mclust::adjustedRandIndex(mbiome_member_8, sn_member_8),
    mclust::adjustedRandIndex(mbiome_member_9, sn_member_9),
    mclust::adjustedRandIndex(mbiome_member_10, sn_member_10),
    mclust::adjustedRandIndex(mbiome_member_11, sn_member_11),
    mclust::adjustedRandIndex(mbiome_member_12, sn_member_12),
    mclust::adjustedRandIndex(mbiome_member_13, sn_member_13),
    mclust::adjustedRandIndex(mbiome_member_14, sn_member_14),
    mclust::adjustedRandIndex(mbiome_member_15, sn_member_15),
    mclust::adjustedRandIndex(mbiome_member_16, sn_member_16),
    mclust::adjustedRandIndex(mbiome_member_17, sn_member_17),
    mclust::adjustedRandIndex(mbiome_member_18, sn_member_18)
  )
)

p_vals <- data.frame(
  vils = observed$vils,
  p_val = c(
    sum(null_clusters$rand_inds[null_clusters$vils ==
                                  observed$vils[1]] >= observed$obs[1]) /
      10000,
    sum(null_clusters$rand_inds[null_clusters$vils ==
                                  observed$vils[2]] >= observed$obs[2]) /
      10000,
    sum(null_clusters$rand_inds[null_clusters$vils ==
                                  observed$vils[3]] >= observed$obs[3]) /
      10000,
    sum(null_clusters$rand_inds[null_clusters$vils ==
                                  observed$vils[4]] >= observed$obs[4]) /
      10000,
    sum(null_clusters$rand_inds[null_clusters$vils ==
                                  observed$vils[5]] >= observed$obs[5]) /
      10000,
    sum(null_clusters$rand_inds[null_clusters$vils ==
                                  observed$vils[6]] >= observed$obs[6]) /
      10000,
    sum(null_clusters$rand_inds[null_clusters$vils ==
                                  observed$vils[7]] >= observed$obs[7]) /
      10000,
    sum(null_clusters$rand_inds[null_clusters$vils ==
                                  observed$vils[8]] >= observed$obs[8]) /
      10000,
    sum(null_clusters$rand_inds[null_clusters$vils ==
                                  observed$vils[9]] >= observed$obs[9]) /
      10000,
    sum(null_clusters$rand_inds[null_clusters$vils ==
                                  observed$vils[10]] >= observed$obs[10]) /
      10000,
    sum(null_clusters$rand_inds[null_clusters$vils ==
                                  observed$vils[11]] >= observed$obs[11]) /
      10000,
    sum(null_clusters$rand_inds[null_clusters$vils ==
                                  observed$vils[12]] >= observed$obs[12]) /
      10000,
    sum(null_clusters$rand_inds[null_clusters$vils ==
                                  observed$vils[13]] >= observed$obs[13]) /
      10000,
    sum(null_clusters$rand_inds[null_clusters$vils ==
                                  observed$vils[14]] >= observed$obs[14]) /
      10000,
    sum(null_clusters$rand_inds[null_clusters$vils ==
                                  observed$vils[15]] >= observed$obs[15]) /
      10000,
    sum(null_clusters$rand_inds[null_clusters$vils ==
                                  observed$vils[16]] >= observed$obs[16]) /
      10000,
    sum(null_clusters$rand_inds[null_clusters$vils ==
                                  observed$vils[17]] >= observed$obs[17]) /
      10000,
    sum(null_clusters$rand_inds[null_clusters$vils ==
                                  observed$vils[18]] >= observed$obs[18]) /
      10000
  )
)

for(i in 1:nrow(p_vals)){
  if(p_vals$p_val[i] == 0){
    p_vals$p_val[i] <- paste0("p <= .0001")
  }
  else{
    p_vals$p_val[i] <- paste0("p = ", p_vals$p_val[i])
  }
}

null_clusters$dummy = null_clusters$rand_inds
```

```{r}
cluster_pvals_fig <- 
  ggplot(null_clusters, aes(x=rand_inds ))+
  geom_histogram(color="black",fill="grey", bins = 100, show.legend = FALSE)+
  #facet_grid(as.factor(vils) ~ .) +
  facet_wrap(~ vils, ncol=2) +
  geom_vline(data=observed,
             aes(xintercept=obs, color="red"),
             linetype="solid", show.legend = FALSE) +
  theme_pubr() +
  ylab("Frequency") +
  xlab("Adjusted Rand Index") +
  ggtitle("Permutation Null Distributions")+
  #scale_x_break(breaks = c(.3,.4), ticklabels=c(-.1,0,.05,.1,.15,.2,.25,.3,.4,.45)) +
  geom_text(data = p_vals, aes(label = p_val,
                               y = 2000,
                               x = .52)) +
  theme_pubr()+
  theme(
    axis.text.x.top = element_blank(),
    axis.ticks.x.top = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_text(size = 10),
    plot.title = element_text(hjust = .5, face = "bold"),
    axis.title  = element_text(face = "bold"),
    axis.text  = element_text(face = "bold")
  ) +
  coord_cartesian(ylim = c(0,4000)) +
  scale_y_continuous(limits = c(0, 4000), breaks = c(0, 2000, 4000))
#Plan el peroicso and mirasol and sesimel
```

Combine with clustering coef bucket fig from centralitysharing
```{r}
ggarrange(cluster_pvals_fig, cluster_bucket_fig, nrow = 1, labels = c("", "h"))
```




Statistics on which relationships are typically grouped together
Probably just following the strain-sharing rate


```{r}
# #Get probability each relationship is grouped together
# #Probably total accuracy
# #Probability of looping in degree two
# #Split up by relationship type
# #Don't really need the SN Clusters
# for(i in 1:length(village_names)) {
#   mbiome_membership <- get(paste0("mbiome_member_", i))
#   #Probability first-degree connections included
#   sn_edges <- get(paste0("sn_vil_", i))
#   for (j in 1:nrow(sn_edges)) {
#     sn_edges$clustered[j] <-
#       mbiome_membership[names(mbiome_membership) == sn_edges$ego[j]] ==
#       mbiome_membership[names(mbiome_membership) == sn_edges$alter[j]]
#   }
#   assign(paste0("sn_vil_", i), sn_edges)
# }
# 
# for(i in 1:length(village_names)) {
#   sn_membership <- get(paste0("sn_member_", i))
#   #Probability first-degree connections included
#   sn_edges <- get(paste0("sn_vil_", i))
#   for (j in 1:nrow(sn_edges)) {
#     sn_edges$clustered_social[j] <-
#       sn_membership[names(sn_membership) == sn_edges$ego[j]] ==
#       sn_membership[names(sn_membership) == sn_edges$alter[j]]
#   }
#   assign(paste0("sn_vil_", i), sn_edges)
# }
# 
# 
# 
# 
# sn_cluster_stack <- rbind(sn_vil_1,
#                           sn_vil_2,
#                           sn_vil_3,
#                           sn_vil_4,
#                           sn_vil_5,
#                           sn_vil_6,
#                           sn_vil_7,
#                           sn_vil_8,
#                           sn_vil_9)
# 
# #Baseline it
# 
# sn_cluster_stack %>%
#   distinct(pair_key,.keep_all = TRUE) %>% 
#   summarize(prob_clustered = mean(clustered))
# 
# sn_cluster_stack %>%
#   distinct(pair_key,.keep_all = TRUE) %>% 
#   summarize(prob_mbiome_clustered = mean(clustered),
#             prob_sn_clustered = mean(clustered_social),
#             prob_overlap = mean(clustered == clustered_social) )
# 
# sn_cluster_stack %>%
#   distinct(relationship, pair_key,.keep_all = TRUE) %>%
#   group_by(relationship) %>% 
#   summarize(prob_clustered = mean(clustered)) %>%
#   arrange(desc(prob_clustered))

```





Village Plots
```{r}

add.alpha <- function(col, alpha = 1) {
  if (missing(col))
    stop("Please provide a vector of colours.")
  apply(sapply(col, col2rgb) / 255, 2,
        function(x)
          rgb(x[1], x[2], x[3], alpha = alpha))
}

pdf('test.pdf')
par(mar=c(0,0,0,0))
for(i in 1:length(village_names)){
  #i<- 1
  #SN_Village <- SN %>% filter(village_name_w3 == village_names[i])
  set.seed(1)
  #min(E(mbiome_all)$weight)
  #mbiome_all <- mbiome_all - E(mbiome_all)[E(mbiome_all)$weight ==0]
  SN_Village <- SN %>% filter(village_code_w3 == village_names[i])
  #Filter to relationships of interest
  #Get ids for that village
  village_ids <- unique(c(SN_Village$ego, SN_Village$alter))
  #mbiome_all <- get(paste0("strain_rate_vil_graph_",i))
  strain_vil <- strain_rate[rownames(strain_rate) %in% village_ids ,
                            colnames(strain_rate) %in% village_ids]
  #Create social network and microbiome networks
  sn_vil <- igraph::simplify(graph_from_data_frame(SN_Village, directed = FALSE))
  
  mbiome_all <- simplify(graph_from_adjacency_matrix(strain_vil,
                                                     mode = "undirected", weighted = TRUE))
  
  #Cluster
  #sum(is.na(E(mbiome_all)$weight))
  mbiome_all <- mbiome_all - E(mbiome_all)[is.na(E(mbiome_all)$weight)]
  mbiome_cluster <- cluster_louvain(mbiome_all, weights = E(mbiome_all)$weight)
  sn_cluster <- cluster_louvain(sn_vil)
  
  max_cluster <- max(max(membership(mbiome_cluster)), max(membership(sn_cluster)))
  
  colors <- pals::cols25(max_cluster)
  colors <- add.alpha(colors, alpha = .5)

  mbiome_cols <- colors[membership(mbiome_cluster)]
  #Want colors here to best visually map to social network
  par(mfrow=c(1,3))
  plot(mbiome_cluster,
       mbiome_all,
       col = mbiome_cols,
       #mark.groups = mbiome_cols,
       mark.col = colors,
       mark.border=colors,
       vertex.label = NA,
       vertex.size =5,
       edge.width=E(mbiome_all)$weight/50,
       edge.color = "black",
       layout = layout_with_fr,
      main = paste(village_names[i], "Strain Clusters")
  )
  # table(membership(sn_cluster))
  # table(membership(mbiome_cluster))
  # temp <- membership(mbiome_cluster)
  # swap <- c(temp)
  # swap <- case_when(
  #   swap == 1 ~ 5,
  #   swap == 5 ~ 2,
  #   swap == 3 ~ 6,
  #   swap == 2 ~ 1,
  #   swap == 4 ~ 3,
  #   TRUE ~ swap
  # )
  # names(swap) <- names(temp)


  
  V(sn_vil)$color <- colors[membership(sn_cluster)]
  set.seed(1)
  sn_colors <- colors[membership(sn_cluster)]
  plot(sn_vil,
       vertex.label = NA,
       vertex.size =5,
       mark.col = colors,
       mark.border=colors,
       col = sn_colors,
       edge.color = "black",
       layout = layout_with_fr,
       main = paste(village_names[i], "Social Network Clusters")
  )

  #Could Change these to match colors, hard would have to do manually
  #V(sn_vil)$color <- swap[match(V(sn_vil)$name, names(swap))]
  V(sn_vil)$color <- membership(mbiome_cluster)[match(V(sn_vil)$name, names(membership(mbiome_cluster)))]
  V(sn_vil)$color <- colors[as.numeric(V(sn_vil)$color)]
  set.seed(1)
  plot(sn_vil,
       vertex.label = NA,
       vertex.size =5,
       edge.color = "black",
       #vertex.color = new_cols,
       layout = layout_with_fr,
      main = paste(village_names[i], "Microbiome Clusters Overlay")
  )
}
dev.off()
#there's a couple good ones I say bring in the old strains for Mariposal
```


Mariposal Visualization
```{r}

add.alpha <- function(col, alpha = 1) {
  if (missing(col))
    stop("Please provide a vector of colours.")
  apply(sapply(col, col2rgb) / 255, 2,
        function(x)
          rgb(x[1], x[2], x[3], alpha = alpha))
}

SN_Village <- SN %>% filter(village_name_w3 == "mariposal")
#Filter to relationships of interest
#Get ids for that village
village_ids <- unique(c(SN_Village$ego, SN_Village$alter))

strain_vil <-
  strain_rate[rownames(strain_rate) %in% village_ids ,
                  colnames(strain_rate) %in% village_ids]
#Create social network and microbiome networks
sn_vil <-
  igraph::simplify(graph_from_data_frame(SN_Village, directed = FALSE))

mbiome_all <-
  simplify(graph_from_adjacency_matrix(strain_vil, mode = "undirected", weighted = TRUE))

#Cluster
mbiome_cluster <-  cluster_louvain(mbiome_all, weights = E(mbiome_all)$weight )
sn_cluster <- cluster_louvain(sn_vil)

max_cluster <-
  max(max(membership(mbiome_cluster)), max(membership(sn_cluster)))

colors <- pals::cols25(max_cluster)


temp <- membership(mbiome_cluster)
swap <- c(temp)
swap <- case_when(swap == 4 ~ 5,
                  swap == 3 ~ 2,
                  swap == 2 ~ 4,
                  swap == 1 ~ 3,
                  TRUE ~ swap)
names(swap) <- names(temp)



V(sn_vil)$color <- colors[membership(sn_cluster)]
sn_colors <- colors[membership(sn_cluster)]
set.seed(1)
plot(
  #sn_cluster,
  sn_vil,
  vertex.label = NA,
  vertex.size = 5,
  mark.col = colors,
  mark.border = colors,
  col = sn_colors,
  edge.color = "black",
  layout = layout_with_fr,
  main = "Social Network Clusters for Mariposal"
)
set.seed(1)
mariposal_sn <- as.ggplot(expression(plot(#sn_cluster,
  sn_vil,
  vertex.label = NA,
  vertex.size = 5,
  mark.col = colors,
  mark.border = colors,
  col = sn_colors,
  edge.color = "black",
  layout = layout_with_fr,
  #main = "Social Network Clusters"
),
title("Social Network Clusters",line = 0)))

#Could Change these to match colors, hard would have to do manually
V(sn_vil)$color <- swap[match(V(sn_vil)$name, names(swap))]
V(sn_vil)$color <- colors[as.numeric(V(sn_vil)$color)]
set.seed(1)

plot(
  sn_vil,
  vertex.label = NA,
  vertex.size = 5,
  edge.color = "black",
  layout = layout_with_fr,
  main = "Microbiome Similarity Clusters\non Social Network"
)
set.seed(1)
mariposal_overlay <- as.ggplot(expression(plot(
  sn_vil,
  vertex.label = NA,
  vertex.size = 5,
  edge.color = "black",
  layout = layout_with_fr#,
  #main = "Microbiome Similarity Clusters\non Social Network"
),
title("Microbiome Similarity Clusters\non Social Network", line = -.75)))

colors <- add.alpha(colors, alpha = .5)
mbiome_cols <- colors[swap]
mbiome_cols_rect <- colors
mbiome_cols_rect <- mbiome_cols_rect[c(3,4,2,5)]
V(mbiome_all)$color <- mbiome_cols

set.seed(1)
plot(
  mbiome_cluster,
  mbiome_all,
  col = mbiome_cols,
  mark.col = mbiome_cols_rect,
  mark.border = mbiome_cols_rect,
  vertex.label = NA,
  vertex.size = 5,
  edge.width = E(mbiome_all)$weight / 25,
  edge.color = "black",
  layout = layout_with_fr,
  main = "Microbiome Similarity Clusters"
)


mariposal_mbiome <- as.ggplot(expression(plot(
  mbiome_cluster,
  mbiome_all,
  col = mbiome_cols,
  mark.col = mbiome_cols_rect,
  mark.border = mbiome_cols_rect,
  vertex.label = NA,
  vertex.size = 5,
  edge.width = E(mbiome_all)$weight / 25,
  edge.color = "black",
  layout = layout_with_fr#,
  #main = "Microbiome Similarity Clusters"
),
title("Microbiome Similarity Clusters",line = 0)))
```

Quesaras Visualization
```{r}
village_map
SN_Village <- SN %>% filter(village_name_w3 == "Hernani")


village_ids <- unique(c(SN_Village$ego, SN_Village$alter))

strain_vil <-
  strain_rate[rownames(strain_rate) %in% village_ids ,
                  colnames(strain_rate) %in% village_ids]

sn_vil <-
  igraph::simplify(graph_from_data_frame(SN_Village, directed = FALSE))

mbiome_all <-
  simplify(graph_from_adjacency_matrix(strain_vil, mode = "undirected", weighted = TRUE))

#Cluster
mbiome_cluster <-
  cluster_louvain(mbiome_all, weights = E(mbiome_all)$weight)
sn_cluster <- cluster_louvain(sn_vil)

max_cluster <-
  max(max(membership(mbiome_cluster)), max(membership(sn_cluster)))

colors <- pals::cols25(max_cluster)


#need to line up the cluster plot now
temp <- membership(mbiome_cluster)
swap <- c(temp)
swap <- case_when(swap == 1 ~ 5,
                  swap == 5 ~ 2,
                  swap == 3 ~ 6,
                  swap == 2 ~ 1,
                  swap == 4 ~ 3,
                  TRUE ~ swap)
names(swap) <- names(temp)



V(sn_vil)$color <- colors[membership(sn_cluster)]
sn_colors <- colors[membership(sn_cluster)]
set.seed(1)
plot(#sn_cluster,
  sn_vil,
  vertex.label = NA,
  vertex.size = 5,
  mark.col = colors,
  mark.border = colors,
  col = sn_colors,
  edge.color = "black",
  layout = layout_with_fr
)
set.seed(1)
quesaras_sn <- as.ggplot(expression(plot(#sn_cluster,
  sn_vil,
  vertex.label = NA,
  vertex.size = 5,
  mark.col = colors,
  mark.border = colors,
  col = sn_colors,
  edge.color = "black",
  layout = layout_with_fr,
  #main = "Social Network Clusters"
),
title("Social Network Clusters")))

#Could Change these to match colors, hard would have to do manually
V(sn_vil)$color <- swap[match(V(sn_vil)$name, names(swap))]
#V(sn_vil)$color <- membership(mbiome_cluster)[match(V(sn_vil)$name, names(membership(mbiome_cluster)))]
V(sn_vil)$color <- colors[as.numeric(V(sn_vil)$color)]
set.seed(1)
plot(
  sn_vil,
  vertex.label = NA,
  vertex.size = 5,
  edge.color = "black",
  layout = layout_with_fr,
  main = "Microbiome Similarity Clusters\non Social Network"
)
set.seed(1)
quesaras_overlay <- as.ggplot(expression(plot(
  sn_vil,
  vertex.label = NA,
  vertex.size = 5,
  edge.color = "black",
  layout = layout_with_fr,
  #main = "Microbiome Similarity Clusters\non Social Network"
),
title("Microbiome Similarity Clusters\non Social Network")))
colors <- add.alpha(colors, alpha = .5)
mbiome_cols <- colors[swap]
mbiome_cols_rect <- colors
mbiome_cols_rect <- mbiome_cols_rect[c(5,1,6,3,2)]

V(mbiome_all)$color <- mbiome_cols

plot(
  mbiome_cluster,
  mbiome_all,
  col = mbiome_cols,
  mark.col = mbiome_cols_rect,
  mark.border = mbiome_cols_rect,
  vertex.label = NA,
  vertex.size = 5,
  edge.width = E(mbiome_all)$weight / 25,
  edge.color = "black",
  layout = layout_with_fr
)

quesaras_mbiome <- as.ggplot(expression(plot(
  mbiome_cluster,
  mbiome_all,
  col = mbiome_cols,
  mark.col = mbiome_cols_rect,
  mark.border = mbiome_cols_rect,
  vertex.label = NA,
  vertex.size = 5,
  edge.width = E(mbiome_all)$weight / 25,
  edge.color = "black",
  layout = layout_with_fr,
  #main = "Microbiome Similarity Clusters"
),
title("Microbiome Similarity Clusters")))

```

create_figure
```{r}
library(ggpubr)
ggarrange(cluster_pvals_fig, cluster_bucket_fig, nrow = 1, labels = c("g", "h"))



fig5_1 <- ggarrange(cluster_bucket_fig,
          mariposal_mbiome,
          labels = c("A", "B"),
          nrow = 1)

fig5_2 <- ggarrange(mariposal_sn,
          mariposal_overlay,
          labels = c("C", "D"),
          nrow = 1)

#Need to get this from the species_niches script
fig5_3<- ggarrange(species_da_1, species_da_2,
          labels = c("F", "G"), nrow = 1)

fig5_4 <- ggarrange(fig5_1,
                    fig5_2,
                    fig5_3,
                    nrow = 3)

fig5 <- ggarrange(fig5_4,
                  ggarrange(cluster_pvals_fig, labels = "E"),
                  widths = c(2,1),
                  nrow = 1)





svglite("../FiguresNew/Figure5/fig5_full_new_2.svg",
        width = 12,
        height = 12)
fig5
dev.off()

```


```{r}
ggarrange(cluster_bucket_fig,
          mariposal_mbiome,
          mariposal_sn,
          mariposal_overlay,
          labels = c("A", "B",
                     "C", "D"), nrow = 2)

mariposal_cluster_fig <-ggarrange(mariposal_mbiome, mariposal_sn, mariposal_overlay,
                                  nrow = 1, labels = c("A", "C", "E"))

quesaras_cluster_fig <-ggarrange(quesaras_mbiome, quesaras_sn, quesaras_overlay,
                                  nrow = 1, labels = c("B", "D", "F"))

ggarrange(mariposal_cluster_fig, quesaras_cluster_fig, nrow = 2)

cluster_overlap_fig <- ggarrange(mariposal_mbiome, mariposal_overlay, mariposal_sn,
                                 quesaras_mbiome, quesaras_overlay, quesaras_sn,
                                 nrow = 2, labels = c("a", "b", "c", "d", "e", "f"))
```



Test Visualization
```{r}
village_map
village_names
plot(sn_vil_graph_8,vertex.label = NA,
  vertex.size = 5)

sn_vil <- sn_vil_graph_8

mbiome_all <- strain_rate_vil_graph_8

# plot(sn_cluster_8,
#   sn_vil_graph_8,
#   vertex.label = NA,
#   vertex.size = 5,
#   mark.col = colors,
#   mark.border = colors,
#   col = sn_colors,
#   edge.color = "black",
#   layout = layout_with_fr
# )
# 
# SN_Village <- SN %>% filter(village_name_w3 == "Plan El Perico")
# 
# village_ids <- unique(c(SN_Village$ego, SN_Village$alter))
# 
# strain_vil <-
#   strain_rate[rownames(strain_rate) %in% village_ids ,
#                   colnames(strain_rate) %in% village_ids]
# 
# sn_vil <-
#   igraph::simplify(graph_from_data_frame(SN_Village, directed = FALSE))
# 
# mbiome_all <-
#   simplify(graph_from_adjacency_matrix(strain_vil, mode = "undirected", weighted = TRUE))

#Cluster
mbiome_cluster <-
  cluster_louvain(mbiome_all, weights = E(mbiome_all)$weight)
sn_cluster <- cluster_louvain(sn_vil)

max_cluster <-
  max(max(membership(mbiome_cluster)), max(membership(sn_cluster)))

colors <- pals::cols25(max_cluster)




V(sn_vil)$color <- colors[membership(sn_cluster)]
sn_colors <- colors[membership(sn_cluster)]
set.seed(1)
plot(#sn_cluster,
  sn_vil,
  vertex.label = NA,
  vertex.size = 5,
  mark.col = colors,
  mark.border = colors,
  col = sn_colors,
  edge.color = "black",
  layout = layout_with_fr
)


#Could Change these to match colors, hard would have to do manually
#V(sn_vil)$color <- swap[match(V(sn_vil)$name, names(swap))]
V(sn_vil)$color <- membership(mbiome_cluster)[match(V(sn_vil)$name, names(membership(mbiome_cluster)))]
V(sn_vil)$color <- colors[as.numeric(V(sn_vil)$color)]
set.seed(1)
plot(
  sn_vil,
  vertex.label = NA,
  vertex.size = 5,
  edge.color = "black",
  layout = layout_with_fr,
  main = "Microbiome Similarity Clusters\non Social Network"
)
set.seed(1)
quesaras_overlay <- as.ggplot(expression(plot(
  sn_vil,
  vertex.label = NA,
  vertex.size = 5,
  edge.color = "black",
  layout = layout_with_fr,
  #main = "Microbiome Similarity Clusters\non Social Network"
),
title("Microbiome Similarity Clusters\non Social Network")))
colors <- add.alpha(colors, alpha = .5)
mbiome_cols <- colors[swap]
mbiome_cols_rect <- colors
mbiome_cols_rect <- mbiome_cols_rect[c(5,1,6,3,2)]

V(mbiome_all)$color <- mbiome_cols

plot(
  mbiome_cluster,
  mbiome_all,
  col = mbiome_cols,
  mark.col = mbiome_cols_rect,
  mark.border = mbiome_cols_rect,
  vertex.label = NA,
  vertex.size = 5,
  edge.width = E(mbiome_all)$weight / 25,
  edge.color = "black",
  layout = layout_with_fr
)

quesaras_mbiome <- as.ggplot(expression(plot(
  mbiome_cluster,
  mbiome_all,
  col = mbiome_cols,
  mark.col = mbiome_cols_rect,
  mark.border = mbiome_cols_rect,
  vertex.label = NA,
  vertex.size = 5,
  edge.width = E(mbiome_all)$weight / 25,
  edge.color = "black",
  layout = layout_with_fr,
  #main = "Microbiome Similarity Clusters"
),
title("Microbiome Similarity Clusters")))

```



