---
title: "Longitudinal Analysis"
author: "Francesco Beghini"
date: "2023-10-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, warning = FALSE, message = FALSE, cache.lazy = FALSE)
library(stringi)
library(stringr)
library(dplyr)
library(readr)
library(igraph)
library(doParallel)
library(foreach)
library(ggplot2)
library(tidyr)
library(lmerTest)
library(lme4)
```

```{r load_metadata_microbiome, message=FALSE, warning=FALSE}
metadata_followup <- read_csv('~/F_BEGHINI_HM/COHORT1_FOLLOWUP/v2/hmb_respondents_cohort1_followup_v2_f_beghini_2022-11-08.csv', na = c('NA','Dont_Know','Refused'),show_col_types = FALSE) |> 
  mutate(mb_m05 = str_replace(mb_m00, '-00$', '-15'),
  marital_name = if_else(!is.na(mb_c004),mb_c004, 'Married')) |> 
  filter(!is.na(mb_m05)) |> 
  mutate(BMI = (mb_d0100 / mb_d0200 **2) * 10000)

metadata_baseline <- read_csv('~/F_BEGHINI_HM/COHORT1/v3/hmb_respondents_cohort1_baseline_v3_f_beghini_2022-11-08.csv', na = c('NA','Dont_Know','Refused'),show_col_types = FALSE) |> 
  filter(respondent_master_id %in% metadata_followup$respondent_master_id,
         !is.na(mb_m05)) |> 
    mutate(BMI = (mb_d0100 / mb_d0200 **2) * 10000)



subset_samples_fw <- c(metadata_followup$mb_m05, metadata_baseline$mb_m05)

master_key_fw <- bind_rows(metadata_baseline,metadata_followup) |> dplyr::select(mb_m05, respondent_master_id, village_code) |> tibble::column_to_rownames('mb_m05')
```

```{r load_social_network_waves, message=FALSE, warning=FALSE}
SN_w1 <- read_csv("~/F_BEGHINI_G/WAVE1/v8/honduras_connections_WAVE1_v8_F_BEGHINI_2023-11-01.csv",show_col_types = FALSE) |> 
              filter(relationship %in% c('child_over12_other_house','closest_friend','father','free_time','mother','partner','personal_private','sibling'), #Remove not get along
                     ego %in% metadata_followup$respondent_master_id, 
                     alter %in% metadata_followup$respondent_master_id,
                     ego %in% metadata_baseline$respondent_master_id, 
                     alter %in% metadata_baseline$respondent_master_id
                     ) |>
              mutate(pair = vapply(stri_split_boundaries(str_c(ego, alter), type='character'), function(x) stri_c(x[stri_order(x)], collapse = ''), ''),
                     wave = 1)

reduced_SN_w1 <- SN_w1 |> 
  group_by(pair) |> 
  summarize(ego, alter, relationship = paste(relationship, collapse = ','), across(starts_with('a2703'), ~ paste(unique(.x[!is.na(.x)]), collapse = ',')) , village_name_w1, village_code_w1) |> 
  distinct(pair, .keep_all = TRUE) |> 
  mutate(is_kin = grepl('mother|father|child|sibling', relationship)) |> 
  dplyr::select(ego, alter, everything()) |> 
  ungroup()

SN_w3 <- read_csv("~/F_BEGHINI_G/WAVE3/v3/honduras_connections_WAVE3_v3_F_BEGHINI_2021-09-27.csv", guess_max = 50000,show_col_types = FALSE) |> 
              filter(relationship %in% c('child_over12_other_house','closest_friend','father','free_time','mother','partner','personal_private','sibling'), #Remove not get along
                     ego %in% metadata_followup$respondent_master_id, 
                     alter %in% metadata_followup$respondent_master_id,
                     ego %in% metadata_baseline$respondent_master_id, 
                     alter %in% metadata_baseline$respondent_master_id
                     ) |> 
                mutate(pair = vapply(stri_split_boundaries(str_c(ego, alter), type='character'), function(x) stri_c(x[stri_order(x)], collapse = ''), ''),
                       wave = 3)

SN_w4 <- read_csv("~/F_BEGHINI_G/WAVE4/v1/honduras_connections_WAVE4_v1_F_BEGHINI_2023-11-01.csv", guess_max = 50000,show_col_types = FALSE) |> 
              filter(relationship %in% c('child_over12_other_house','closest_friend','father','free_time','mother','partner','personal_private','sibling'), #Remove not get along
                     ego %in% metadata_followup$respondent_master_id, 
                     alter %in% metadata_followup$respondent_master_id) |> 
                mutate(pair = vapply(stri_split_boundaries(str_c(ego, alter), type='character'), function(x) stri_c(x[stri_order(x)], collapse = ''), ''),
                       wave = 4)
respondents_w4 <- read_csv('~/F_BEGHINI_G/WAVE4/v1/honduras_respondents_WAVE4_v1_F_BEGHINI_2023-11-01.csv', guess_max = 50000,show_col_types = FALSE) |> 
              filter(respondent_master_id %in% metadata_followup$respondent_master_id)
```

```{r collapse_multiple_ties}
reduced_SN_w3 <- SN_w3 |> 
  unite(a2703a, a2703a, a2704a, na.rm = TRUE,) |> 
  unite(a2703b, a2703b, a2704b, na.rm = TRUE,) |> 
  unite(a2703c, a2703c, a2704c, na.rm = TRUE,) |> 
  unite(a2703d, a2703d, a2704d, na.rm = TRUE,) |> 
  unite(a2703e, a2703e, a2704e, na.rm = TRUE,) |> 
  unite(a2703f, a2703f, a2704f, na.rm = TRUE,) |> 
  unite(a2703g, a2703g, a2704g, na.rm = TRUE,) |> 
  mutate(across(starts_with('a2703'), ~ na_if(.x, ''))) |> 
  select(-a2703, -a2704, -question,-a2703h, -alter_source, -office_w3, -municipality_w3) |> 
  group_by(pair) |> 
  summarize(ego, alter, relationship = paste(relationship, collapse = ','), across(starts_with('a2703'), ~ paste(unique(.x[!is.na(.x)]), collapse = ',')) , village_name_w3, village_code_w3) |> 
  distinct(pair, .keep_all = TRUE) |> 
  mutate(is_kin = grepl('mother|father|child|sibling', relationship)) |> 
  select(ego, alter, everything()) |> 
  ungroup()

SN_w3_graph <- graph_from_data_frame((reduced_SN_w3 |> select(-village_name_w3, -village_code_w3)), 
                                     directed = FALSE, 
                                     vertices = (reduced_SN_w3 |> 
                                                   select(ego, alter, starts_with('village')) |> 
                                                   pivot_longer(cols = c(-village_name_w3, -village_code_w3), names_to = 'a', values_to = 'vertex') |> 
                                                   select(vertex, starts_with('village')) |> 
                                                   distinct()
                                                 )
                                     )

SN_w1_graph <- graph_from_data_frame((reduced_SN_w1 |> select(-village_code_w1, -village_name_w1)),
                                     directed = FALSE,
                                     vertices = (reduced_SN_w1 |> 
                                                   select(ego, alter, starts_with('village')) |> 
                                                   pivot_longer(cols = c(-village_name_w1, -village_code_w1), names_to = 'a', values_to = 'vertex') |> 
                                                   select(vertex, starts_with('village')) |> 
                                                   distinct()
                                                 )
                                     )

```


```{r load_strainphlan_data, cache=FALSE}
strain_shared <- readRDS('/SCRATCH/tmp/shared.RDS')  |> 
    filter(s1 %in% subset_samples_fw & s2 %in% subset_samples_fw ) |> 
    mutate(ego = master_key_fw[s1, 'respondent_master_id' ],
         alter = master_key_fw[s2, 'respondent_master_id'],
         pair = vapply(stri_split_boundaries(str_c(ego, alter), type='character'), function(x) stri_c(x[stri_order(x)], collapse = ''), ''),
         timepoint = case_when( 
           str_sub(s1,10)=='05' & str_sub(s2,10) == '05' ~ 'T1',
           str_sub(s1,10)=='15' & str_sub(s2,10) == '15' ~ 'T2',
           str_sub(s1,10)=='05' & str_sub(s2,10) == '15' ~ 'T1/T2',
           str_sub(s1,10)=='15' & str_sub(s2,10) == '05' ~ 'T2/T1',
           )
         ) |> 
  left_join(SN_w3, by = join_by(pair))

sharing_rate <- readRDS('/SCRATCH/tmp/sharing_rate_with_zero_long_with_followup.RDS') |> 
  separate_wider_delim(pair, "=", names = c('s1','s2')) |> 
  filter(s1 %in% subset_samples_fw & s2 %in% subset_samples_fw ) |> 
  mutate(ego = master_key_fw[s1, 'respondent_master_id' ],
         alter = master_key_fw[s2, 'respondent_master_id'],
           pair = vapply(stri_split_boundaries(str_c(ego, alter), type='character'), function(x) stri_c(x[stri_order(x)], collapse = ''), ''),
         same_subject = str_sub(s1,1,8) == str_sub(s2,1,8),
         village_code_ego = master_key_fw[s1, 'village_code'],
         village_code_alter = master_key_fw[s2, 'village_code']
  )

sharing_rate_T1_w3 <- sharing_rate |> 
  filter(timepoint=='T1') |> 
  left_join(SN_w3, by = join_by(pair, alter, ego))

sharing_rate_T2_w3 <- sharing_rate |> 
  filter(timepoint=='T2') |> 
  left_join(SN_w3, by = join_by(pair, alter, ego))

sharing_rate_inter <- sharing_rate |> 
  filter(timepoint=='T1/T2')

sharing_w3 <- strain_shared 

```

```{r edge_change_t1_t2, cache=FALSE}
cluster <- multidplyr::new_cluster(20)
multidplyr::cluster_library(cluster, "dplyr")
status_sharing_w3 <- sharing_w3 |> 
  filter(same_timepoint==TRUE) |> 
  select(s1,s2, pair, dist, species, timepoint, relationship=relationship.x, shared ) |> 
  distinct(pair, species, relationship, timepoint, .keep_all = TRUE) |> 
  arrange(species, timepoint) |> 
  group_by(pair, species, relationship) |> 
  multidplyr::partition(cluster) |> 
  summarise(status = dplyr::case_when(
    n() == 1 & timepoint=='T1' & shared == TRUE ~ 'sharing_lost_at_t2',
    n() == 1 & timepoint=='T2' & shared == TRUE ~ 'sharing_acquired_only_at_t2',
    n() == 2 & shared == TRUE                   ~ 'kept_sharing',
    .default = 'no_share'
  )) |> 
  collect()
```
```{r include=FALSE}
sharing_w3 |> 
  filter(same_subject==TRUE) |> 
  mutate(trans = dist <= threshold) |> 
  mutate(timepoint = 'Intra-timepoint') |>
  group_by(pair, timepoint, village_code_w3) |>  
  summarize(ssr=sum(trans==TRUE)/n()) |> 
  ggplot() + 
    geom_boxplot(aes(village_code_w3, ssr))
    #ggbeeswarm::geom_quasirandom(aes(timepoint, ssr))
```


```{r eval=FALSE, include=FALSE}
status_sharing_w3 |> 
  distinct() |> 
  filter(!is.na(relationship)) |> 
  ggplot(aes(relationship, fill=status)) +
  geom_bar(position="stack", stat="count")
```

```{r eval=FALSE, include=FALSE}
status_sharing_w3 |> 
  sample_n(100)
  distinct() |> 
  filter(!is.na(relationship)) |> 
  pivot_wider(-status)
  group_by(pair) |> 
  summarize()
```
```{r eval=FALSE, include=FALSE}
cols = c('T1'=NA,'T2'=NA,'T1/T2'=NA,'T2/T1'=NA)
all_pairs <- foreach(ego_l = c(SN_w3$ego, SN_w3$alter), .combine = 'rbind') %do% {
  ego_n = make_ego_graph(SN_w3_graph, nodes = ego_l, mindist = 0)[[1]]
  foreach(alter_l = setdiff(names(V(ego_n)), ego_l), .combine = 'rbind') %do%{
    pair_l = stri_c(stri_sort(stri_split_boundaries(str_c(ego_l, alter_l), type='character')[[1]]), collapse = '')
    c(pair_l, ego_l, alter_l)
  } 
}
colnames(all_pairs) = c('pairs','ego','alter')
all_pairs <- as.data.frame(all_pairs) |> 
  distinct(pairs, .keep_all = TRUE)

cl <- parallel::makeForkCluster(12)
doParallel::registerDoParallel(cl)

longitudinal_ds <- foreach(row = rownames(all_pairs), .combine = 'rbind') %dopar% {
  pair_l = all_pairs[row,'pairs']
  ego_l = all_pairs[row,'ego']
  alter_l = all_pairs[row,'alter']
  ego_kept_strain_overtime = strain_shared |> filter(ego==ego_l&alter==ego_l) |> select(-same_village,-threshold)
  alter_kept_strain_overtime = strain_shared |> filter(ego==alter_l & alter==alter_l) |> select(-same_village,-threshold)
    tmp <- strain_shared |> filter(pair == pair_l) |> 
      pivot_wider(id_cols = everything(), names_from = timepoint, values_from = shared)
    
     tmp <- tibble::add_column(tmp, !!!cols[setdiff(names(cols),names(tmp))]) |> 
      group_by(pair, species) |>
      summarise(T1 = sum(T1, na.rm = TRUE), 
                T2 = sum(T2, na.rm = TRUE),
                `T1/T2` = sum(`T1/T2`, na.rm = TRUE),
                `T2/T1` = sum(`T2/T1`, na.rm = TRUE)
                ) |> 
      arrange(species) |> 
      left_join(ego_kept_strain_overtime |> filter(ego == ego_l) |> select(species, ego_kept=shared), by=join_by(species)) |> 
      left_join(alter_kept_strain_overtime |> filter(alter == alter_l) |> select(species, alter_kept=shared), by=join_by(species)) |> 
      mutate(across(where(is.logical), ~ if_else(is.na(.x), 0, as.integer(.x)))) |> 
       ungroup()

     tmp
  
}
parallel::stopCluster(cl)
```

```{r eval=FALSE, include=FALSE}
longitudinal_ds |> 
  ungroup() |> 
  mutate(trans_only_t1 = as.integer(T1==1 & rowSums(across(starts_with('T')))==1 & rowSums(across(contains('_kept'))) == 0),
         trans_only_t2 = as.integer(T2==1 & rowSums(across(starts_with('T')))==1 & rowSums(across(contains('_kept'))) == 0),
         retained = as.integer(T1 == 1 & T2 == 1 & rowSums(across(contains('_kept'))) == 2 & rowSums(across(contains('/'))) ==2 )
         ) |> 
  group_by(pair) |> 
  summarize(srr = sum(retained) / n(),
            ssr_t1 = sum(T1) / n(),
            ssr_t2 = sum(T2) / n()) |> 
  left_join(SN_w3, by=join_by(pair)) |> 
  select(pair, relationship, srr, ssr_t1, ssr_t2) |> 
  pivot_longer(cols = 3:5, names_to = 'rate', values_to = 'value') |> 
  ggplot() +
  geom_boxplot(aes(relationship, value, fill=rate))
```


```{r eval=FALSE, include=FALSE}
# Cosine similarity species
cosine_dis_long <- lsa::cosine(as.matrix(species_data)) |> 
  as.data.frame() |> 
  tibble::rownames_to_column('s') |> 
  pivot_longer(-s, names_to = 's1', values_to = 'cos')

species_bray_long <- species_bray |> 
  as.data.frame() |> 
  tibble::rownames_to_column('s') |> 
  pivot_longer(-s, names_to = 's1', values_to = 'bc')
```


```{r}
demographics <- read_csv("/WORKAREA/work/HONDURAS_MICROBIOME/J_PULLMAN/DATA/COHORT_1/v2/honduras_respondents_demographics_J_PULLMAN_2022-11-07.csv")



household_wealth_data2 <- read.csv("~/F_BEGHINI_G/WAVE3/v3/honduras_households_WAVE2_v5_F_BEGHINI_2022-11-01.csv") |> 
  dplyr::select(building_id, l0400, household_wealth_index_w2)

household_wealth_data1 <- read.csv("~/F_BEGHINI_G/WAVE3/v3/honduras_households_WAVE1_v8_F_BEGHINI_2022-11-01.csv") |> 
  dplyr::select(building_id, l0400)

household_wealth_data <- read.csv("~/F_BEGHINI_G/WAVE3/v3/honduras_households_WAVE3_v3_F_BEGHINI_2023_10-23.csv") |> 
              dplyr::select(building_id, l0400, household_wealth_index_w3)

covariates <- inner_join(metadata_baseline, demographics, by="respondent_master_id") |> 
  inner_join(household_wealth_data) |> 
  mutate(across(starts_with('mb_ca'), ~ case_when(as.integer(factor(.x)) / 3 == 1 ~ 1, .default = 0  ))) |>
  mutate(dds_Cereals = as.integer(mb_ca0200|mb_ca0300|mb_ca0400),
         dds_Vegetables = mb_ca1000,
         dds_Fruits = as.integer(mb_ca1100|mb_ca1200),
         dds_Meat_poultry_offal = as.integer(mb_ca1300 |mb_ca1400),
         dds_Eggs = mb_ca0900,
         dds_Fish_seafood = mb_ca1600,
         dds_Legumes = mb_ca0100,
         dds_Dairy = as.integer(mb_ca0500 | mb_ca0600 | mb_ca0700 | mb_ca0800),
         dds_Fats = as.integer(mb_ca1500 | mb_ca1900),
         dds_Sugar = as.integer(mb_ca1700 | mb_ca1800),
         DDS = rowSums(across(starts_with('dds_')))
  )
sub_covar <- covariates |> 
  filter(respondent_master_id %in% metadata_followup$respondent_master_id) |> 
  unite('indigenous_status', mb_a0500a:mb_a0500i, na.rm = TRUE) |> 
  dplyr::select(respondent_master_id,
                BMI, 
                gender = gender.x,
                indigenous_status, 
                age_at_survey = age_at_survey.x, 
                DDS, 
                household_wealth_index_w3,
                religion = b0600,
                education = b0100,
                ) |> 
    mutate(education = recode(education, "Have not completed any type of school" = 0,
                                "1st grade" = 1, "2nd grade" = 2, "3rd grade" = 3,
                                "4th grade" = 4, "5th grade" = 5, "6th grade" = 6,
                                "Some secondary" = 7, "Secondary" = 8, "More than secondary" = 9),
           religion = recode(religion, "Catholic" = 1, "No Religion" = 0, "Protestant" =2 )
    )

sub_covar[sub_covar$respondent_master_id=='145q-7f4867c7-a4e1-47e8-9b7c-2d98a4294cdb','household_wealth_index_w3'] <- 5
sub_covar[sub_covar$respondent_master_id=='nZno-6b2d0c05-ebeb-464b-836e-31493a161740','household_wealth_index_w3'] <- 4
sub_covar[sub_covar$respondent_master_id=='cPP0-b47b9cbf-eeaf-430a-87bf-d6322e65108b','household_wealth_index_w3'] <- 2
sub_covar[sub_covar$respondent_master_id=='nZno-b1e42724-5fd4-4aad-8835-80e8a7f430bf','household_wealth_index_w3'] <- 2
sub_covar[sub_covar$respondent_master_id=='enz0-ce7dad59-da03-48d6-9649-40202eba50aa','household_wealth_index_w3'] <- 4
sub_covar[sub_covar$respondent_master_id=='enz0-54c4a166-642d-4707-9dd9-eac58c3452b0','household_wealth_index_w3'] <- 4
sub_covar[sub_covar$respondent_master_id=='cPP0-e7a61fe3-ea87-4f76-b992-bbfbde75393c','household_wealth_index_w3'] <- 4
sub_covar[sub_covar$respondent_master_id=='h4Ru-14c55d32-c61c-44da-9088-6559224a1ae9','household_wealth_index_w3'] <- 3
sub_covar[sub_covar$respondent_master_id=='nZno-66d3906b-0036-4943-bfbb-f5aabaa16123','household_wealth_index_w3'] <- 4
sub_covar[sub_covar$respondent_master_id=='cPP0-00ea6c4f-769a-4670-b7af-cc82af90a235','household_wealth_index_w3'] <- 4
sub_covar[sub_covar$indigenous_status == '','indigenous_status'] = 'None of the above'
sub_covar$indigenous_status <- ifelse(sub_covar$indigenous_status=='None of the above', 0, 1)
sub_covar$genderm <- ifelse(sub_covar$gender == 'man', 1, 0)

sub_covar_mat <- sub_covar |> 
  select(-gender) |> 
  tibble::column_to_rownames('respondent_master_id')
pairwise_mahalanomis <- biotools::D2.dist(sub_covar_mat, cov = cov(sub_covar_mat, use='complete'))
pairwise_mahalanomis |> 
  as.matrix() |> as.data.frame() |>
  tibble::rownames_to_column('s1') |>
  pivot_longer(-s1, names_to = 's2', values_to = 'maha_dist') |> 
  rowwise() |> 
  mutate(pair = stri_c(stri_sort(stri_split_boundaries(str_c(s1, s2), type='character')[[1]]), collapse = '')) |> 
  distinct(pair, .keep_all = TRUE)-> pairwise_mahalanomis_long
```


```{r}
strain_shared_only_relation <- subset(strain_shared, pair %in% reduced_SN_w3$pair)
strain_shared_only_relation$tanh_r <- tanh(strain_shared_only_relation$threshold/strain_shared_only_relation$dist)
```

```{r}
x <- sharing_w3 |> 
  filter(same_subject == FALSE) |> 
  dplyr::select(ego = ego.x, alter = alter.x, pair, relationship = relationship, timepoint, species, threshold, dist) |> 
  distinct(pair, relationship, timepoint, species, .keep_all = TRUE) |> 
  mutate(#tanh_r = tanh(threshold/dist),
         relationship = replace_na(relationship, 'none')) |> 
  pivot_wider(names_from = 'timepoint', values_from = 'dist') |> 
  mutate(across(starts_with('T'), ~ replace_na(.x, 0))
         )

intra_distances <- sharing_w3 |> 
  filter(same_subject==TRUE) |> 
  mutate(#tanh_r = tanh(threshold/dist), 
         timepoint ='intra'
       ) |> 
  pivot_wider(names_from = 'timepoint', values_from = 'dist') |> 
  dplyr::select(respondent_master_id=ego.x, species, intra) 

xcov <- merge(merge(x, sub_covar, by.x = "ego", by.y = 'respondent_master_id', ), sub_covar, by.x = 'alter', by.y = 'respondent_master_id', suffixes = c('_ego','_alter'))

xcov <- merge(merge(xcov, intra_distances, by.x = c("ego",'species'), by.y = c('respondent_master_id','species'), all.x = TRUE), intra_distances, by.x =c('alter', 'species'), by.y =c('respondent_master_id', 'species'), suffixes = c('_ego','_alter'), all.x=TRUE)

xcov$intra_alter[is.na(xcov$intra_alter)] <- 0
xcov$intra_ego[is.na(xcov$intra_ego)] <- 0

xcov$gender.mm <- xcov$gender_ego == "man" & xcov$gender_alter == "man"
xcov$gender.mf <- xcov$gender_ego == "man" & xcov$gender_alter == "woman" | xcov$gender_ego == "woman" & xcov$gender_alter == "man"
xcov$gender.ff <- xcov$gender_ego == "woman" & xcov$gender_alter == "woman"
xcov$indigenous.both <- xcov$indigenous_status_ego != 0 & xcov$indigenous_status_alter != 0
xcov$indigenous.one <- xcov$indigenous_status_ego == 0 & xcov$indigenous_status_alter != 0 | xcov$indigenous_status_ego != 0 & xcov$indigenous_status_alter == 0
xcov$indigenous.none <- xcov$indigenous_status_ego == 0 & xcov$indigenous_status_alter == 0
xcov$age_difference_abs <- abs(xcov$age_at_survey_ego - xcov$age_at_survey_alter)
xcov$average_age <- (xcov$age_at_survey_ego + xcov$age_at_survey_alter)/2
xcov$wealth_difference_abs <- abs(xcov$household_wealth_index_w3_ego - xcov$household_wealth_index_w3_alter)
xcov$average_wealth <- (xcov$household_wealth_index_w3_ego + xcov$household_wealth_index_w3_alter)/2
xcov$DDS_difference_abs <- abs(xcov$DDS_ego - xcov$DDS_alter)
xcov$DDS_average <- (xcov$DDS_ego + xcov$DDS_alter)/2
xcov$education_difference_abs <- abs(education_ego - education_alter)
xcov$average_education <- (education_ego + education_alter)/2

colnames(xcov)[8] <- 'T2T1'
colnames(xcov)[9] <- 'T1T2'

xcov$T1_t <- xcov$T1 < xcov$threshold
xcov$T2_t <- xcov$T2 < xcov$threshold
xcov$T1T2_t <- xcov$T1T2 < xcov$threshold
xcov$T2T1_t <- xcov$T2T1 < xcov$threshold
xcov$intra_ego_t <- xcov$intra_ego < xcov$threshold
xcov$intra_alter_t <- xcov$intra_alter < xcov$threshold

xcov$relationship <- ifelse(xcov$relationship == 'none', FALSE, TRUE)
xcov <- merge(xcov, pairwise_mahalanomis_long, by = 'pair')
```


# Mixed effect model

T1, T2, T1T2, T2T1 are the genetic distances between the pair, the distances are calculated as the species-specific threshold divided by the raw genetic distance, then squeezed between 0 and 1 using tanh().

T1T2 and T2T1 are the pairwise distances between the two strains across the two timepoints.

intra_ego and intra_alter are the intra individual distance across the timepoints, calculated same as T1.

In this model, T2 is used as outcome, all the other distances are then included as interaction terms plus the confounders.

All the distances are significant, but I don’t feel that having the species split and as a random effect  is somehow meaningful.


```{r}
 # relationship + gender.mm + gender.ff + indigenous.both + indigenous.one + age_difference_abs + average_age + average_age + DDS_difference_abs 
glmer(data = xcov, T2_t ~ T1_t*T2T1_t*T1T2_t*intra_ego_t*intra_alter_t + maha_dist + relationship + (1|species), family = binomial, nAGQ=0) -> lmer_species_rand
```

```{r}
summary(lmer_species_rand)
```


```{r}
library(caret)

cl <- parallel::makeCluster(5)
doParallel::registerDoParallel(cl)
foreach(i = c(1:5)) %dopar% {
set.seed(1993)
xcov_inds <- c(1:nrow(xcov))
test_xcov1_inds <- sample(xcov_inds, size = floor(.33*nrow(xcov)), replace = F)
train_xcov1_inds <- xcov_inds[!(xcov_inds %in% test_xcov1_inds)]
test_xcov2_inds <- sample(train_xcov1_inds, size = floor(.5*length(train_xcov1_inds)), replace = F)
train_xcov2_inds <- xcov_inds[!(xcov_inds %in% test_xcov2_inds)]
test_xcov3_inds <- train_xcov2_inds[!(train_xcov2_inds %in% test_xcov1_inds)]
train_xcov3_inds <- xcov_inds[!(xcov_inds %in% test_xcov3_inds)]

test1_xcov <- xcov[test_xcov1_inds,]
train1_xcov <- xcov[train_xcov1_inds,]
test2_xcov <- xcov[test_xcov2_inds,]
train2_xcov <- xcov[train_xcov2_inds,]
test3_xcov <- xcov[test_xcov3_inds,]
train3_xcov <- xcov[train_xcov3_inds,]
  

test1 <- glmer(data = train1_xcov, T2_t ~ T1_t*T2T1_t*T1T2_t*intra_ego_t*intra_alter_t + gender.mm + gender.ff + indigenous.both + indigenous.one + age_difference_abs + average_age + average_age + DDS + relationship + (1|species), family = binomial, nAGQ=0)
test2 <- glmer(data = train2_xcov, T2_t ~ T1_t*T2T1_t*T1T2_t*intra_ego_t*intra_alter_t + gender.mm + gender.ff + indigenous.both + indigenous.one + age_difference_abs + average_age + average_age + DDS + relationship + (1|species), family = binomial, nAGQ=0)
test3 <- glmer(data = train3_xcov, T2_t ~ T1_t*T2T1_t*T1T2_t*intra_ego_t*intra_alter_t + gender.mm + gender.ff + indigenous.both + indigenous.one + age_difference_abs + average_age + average_age + DDS + relationship + (1|species), family = binomial, nAGQ=0)

preds1 <- predict(test1, newdata = test1_xcov, type = "response", allow.new.levels = TRUE)
preds2 <- predict(test1, newdata = test2_xcov, type = "response", allow.new.levels = TRUE)
preds3 <- predict(test3, newdata = test3_xcov, type = "response", allow.new.levels = TRUE)

names(preds1) <- test_xcov1_inds
names(preds2) <- test_xcov2_inds
names(preds3) <- test_xcov3_inds
preds.round <- c(preds1, preds2, preds3)
preds.round <- preds.round[order(as.numeric(names(preds.round)))]

preds.round
} -> preds


pROC::roc(xcov$T2_t, preds, ci=TRUE, plot=FALSE, levels=c(TRUE, FALSE), direction = "<", na.rm=TRUE)

```




# Linear model 

Same model, without the random effect, using lm 

```{r}
glm(data = xcov, T2_t ~ relationship + T1_t*T2T1_t*T1T2_t*intra_ego_t*intra_alter_t+ gender.mm + gender.ff + indigenous.both + indigenous.one + age_difference_abs + average_age + wealth_difference_abs + average_age + DDS_difference_abs) -> lm_all_species
```

```{r}
summary(lm_all_species)
```
```{r}
sharing_rate_pairs_covariates <- sharing_rate |> 
  filter(timepoint !='T1/T2') |> 
  dplyr::select(ego, alter, pair, timepoint, same_subject, village_code_ego, village_code_alter, n1) |> 
  pivot_wider(names_from = timepoint, values_from = n1) |> 
  left_join((xcov |> dplyr::select(pair, relationship, contains('_'), contains('.'), -intra_ego, -intra_alter) |> distinct(pair, .keep_all = TRUE)), by = join_by('pair')) |> 
  left_join((sharing_rate |> filter(same_subject==TRUE) |> dplyr::select(ego, intra=n1)), by = join_by('ego'=='ego')) |> 
  left_join((sharing_rate |> filter(same_subject==TRUE) |> dplyr::select(alter, intra=n1)), by = join_by('alter'=='alter'), suffix = c('_ego','_alter'))

```

```{r}
lmer(data = sharing_rate_pairs_covariates , T2 ~ relationship + T1*intra_ego*intra_alter+ maha_dist + (0+T1|village_code_ego)) -> lm_sharing_rate
```

```{r}
summary(lm_sharing_rate)
```



# Stability w1 w3
```{r overall_stability_across_waves}
pruned_SN_w3_graph <- subgraph(SN_w3_graph, intersect(names(V(SN_w3_graph)),names(V(SN_w1_graph))))
pruned_SN_w1_graph <- subgraph(SN_w1_graph, intersect(names(V(SN_w3_graph)),names(V(SN_w1_graph))))
```

```{r pervillage_stability_across_waves}
foreach(village = unique(reduced_SN_w1$village_code_w1), .combine = rbind) %do% {
  tmp_w3 <- subgraph(pruned_SN_w3_graph, subset(V(pruned_SN_w3_graph), V(pruned_SN_w3_graph)$village_code_w3 == village))
  tmp_w1 <- subgraph(pruned_SN_w1_graph, subset(V(pruned_SN_w1_graph), V(pruned_SN_w1_graph)$village_code_w1 == village))
  data.frame(village_code = as.character(village), stability=length(E(tmp_w3 %s% tmp_w1)) / length(E(tmp_w3 %u% tmp_w1)))
} |> bind_rows(data.frame(village_code = 'overall', stability=length(E(pruned_SN_w3_graph %s% pruned_SN_w1_graph)) / length(E(pruned_SN_w3_graph %u% pruned_SN_w1_graph))))
```

# New egdes in W3
```{r}
new_edges <- igraph::difference(pruned_SN_w3_graph, pruned_SN_w1_graph)
new_edges_attr_df <- data.frame(edge.attributes(new_edges))
nrow(lost_edges_attr_df)
```
# Egdes lost in W3
```{r}
lost_edges <- igraph::difference(pruned_SN_w1_graph, pruned_SN_w3_graph)
lost_edges_attr_df <- data.frame(edge.attributes(lost_edges))
nrow(lost_edges_attr_df)
```

# Number of ties retained
```{r eval=FALSE, include=FALSE}
w1w3_intersection <-  graph.intersection(pruned_SN_w1_graph, pruned_SN_w3_graph, byname = TRUE)
length(E(w1w3_intersection))
```


## Types of new relationships now disclosed in w3
```{r eval=FALSE, include=FALSE}
foreach(e = edge_attr(w1w3_intersection)$pair_1, .combine = c) %do% {
  setdiff(
    reduced_SN_w3 |> filter(pair == e ) |> pull(relationship) |> str_split(pattern = ',', simplify = TRUE) |> c(), 
    reduced_SN_w1 |> filter(pair == e ) |> pull(relationship) |> str_split(pattern = ',', simplify = TRUE) |> c()
  )
} |> table()

```

## Types of relationships not disclosed anymore in w3
```{r eval=FALSE, include=FALSE}
foreach(e = edge_attr(w1w3_intersection)$pair_1, .combine = c) %do% {
  setdiff(
    reduced_SN_w1 |> filter(pair == e ) |> pull(relationship) |> str_split(pattern = ',', simplify = TRUE) |> c(), 
    reduced_SN_w3 |> filter(pair == e ) |> pull(relationship) |> str_split(pattern = ',', simplify = TRUE) |> c()
  )
} |> table()

```
